### 2013-05-06 inst/examples/BUGS/allen.Rmd
replicate runs

```{r plotting-options}
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE, comment=NA,
               fig.width=6, fig.height=4, dev="CairoPDF")

@@

library(ggplot2) # plotting 
#opts_knit$set(upload.fun = socialR::flickr.url)
theme_set(theme_bw(base_size=10))
theme_update(panel.background = element_rect(fill = "transparent", colour = NA),
             plot.background = element_rect(fill = "transparent", colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
               "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```
Load necessary libraries,

>>>>

```{r plotting-options}
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE, comment=NA,
               fig.width=6, fig.height=4)

@@

library(ggplot2) # plotting 
opts_knit$set(upload.fun = socialR::flickr.url)
theme_set(theme_bw(base_size=10))
theme_update(panel.background = element_rect(fill = "transparent", colour = NA),
             plot.background = element_rect(fill = "transparent", colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
               "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```
Load necessary libraries,
